A Data-Driven Framework for Neural Field Modelling

### 2010-11-17 ltx/first_order_framework/LaTeX_Manuscript.tex
deleted Dean comment on the sum of the error in LS

Although the system is nonlinear, the parameters of the system are linear with respect to the state. This is exploited by our procedure where the parameter estimation uses a Least Squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new estimate of the state vector sequence \dean{(this should be mean (not sum) of the squared error for stochastic LS right?)} \ken{why is it different?}. To create the least squares parameter estimator, we first define the $L \times n_{\theta}$ matrix
\begin{equation}
	\mathbf{q}(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \,\textrm{d}\mathbf{r}'.
\end{equation}
Now given a state estimate sequence from the initialisation or an iteration of the URTSS, we can write
\begin{eqnarray*}
	 \hat{\mathbf x}^b_{1} &=& \mathbf{q}(\hat{\mathbf x}^b_0) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_0+\mathbf e_0 \\
	\hat{\mathbf x}^b_{2} &=& \mathbf{q}(\hat{\mathbf x}^b_1) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_1+\mathbf e_1  \\
	&\vdots& \\
	\hat{\mathbf x}^b_{T}&=& \mathbf{q}(\hat{\mathbf x}^b_{T-1}) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_{T-1}+\mathbf e_{T-1}. 
\end{eqnarray*}
This can be written in the compact form
\begin{equation}
	\mathbf Z=\mathbf X \mathcal W+\mathbf{e}, 
\end{equation}
where
\begin{small}
\begin{equation*}
	\mathbf Z=\left[
	\begin{array}{cccc}
		\hat{\mathbf x}^b_{1}\\
		\hat{\mathbf x}^b_{2}\\
		\vdots\\
		\hat{\mathbf x}^b_{T}
	\end{array}
	\right],\quad \mathbf X=\left[
	\begin{array}{cccc}
		\mathbf q(\hat{\mathbf x}^b_0)& \hat{\mathbf x}^b_{0}\\
		\mathbf q(\hat{\mathbf x}^b_1)& \hat{\mathbf x}^b_{1}\\
		\vdots & \vdots\\
		\mathbf q(\hat{\mathbf x}^b_{T-1})& \hat{\mathbf x}^b_{T-1}
	\end{array}
	\right] 
\end{equation*}
\end{small}
and
\begin{small}
\begin{equation*}
\quad \mathcal W=\left[
	\begin{array}{cc}
		\boldsymbol{\theta} \\
		\xi
	\end{array}
	\right],\quad \mathbf{e}=\left[
	\begin{array}{cccc}
		\mathbf e_0\\
		\mathbf e_1\\
		\vdots\\
		\mathbf e_{T-1}
	\end{array}
	\right].
\end{equation*}
\end{small}
Following this, the LS parameter estimates~\cite{Kailath2000} \ken{some reference for this result}, $ \hat{\mathcal{W}}$, are
\begin{equation}
	\hat{\mathcal{W}}=(\mathbf X^\top\mathbf X)^{-1}\mathbf X^\top\mathbf Z. 
\end{equation}

>>>>

Although the system is nonlinear, the parameters of the system are linear with respect to the state. This is exploited by our procedure where the parameter estimation uses a Least Squares (LS) method that minimises the sum of the squared errors (of a predicted state update) with each new estimate of the state vector sequence. To create the least squares parameter estimator, we first define the $L \times n_{\theta}$ matrix
\begin{equation}
	\mathbf{q}(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \,\textrm{d}\mathbf{r}'.
\end{equation}
Now given a state estimate sequence from the initialisation or an iteration of the URTSS, we can write
\begin{eqnarray*}
	 \hat{\mathbf x}^b_{1} &=& \mathbf{q}(\hat{\mathbf x}^b_0) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_0+\mathbf e_0 \\
	\hat{\mathbf x}^b_{2} &=& \mathbf{q}(\hat{\mathbf x}^b_1) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_1+\mathbf e_1  \\
	&\vdots& \\
	\hat{\mathbf x}^b_{T}&=& \mathbf{q}(\hat{\mathbf x}^b_{T-1}) \boldsymbol{\theta}+\xi\hat{\mathbf x}^b_{T-1}+\mathbf e_{T-1}. 
\end{eqnarray*}
This can be written in the compact form
\begin{equation}
	\mathbf Z=\mathbf X \mathcal W+\mathbf{e}, 
\end{equation}
where
\begin{small}
\begin{equation*}
	\mathbf Z=\left[
	\begin{array}{cccc}
		\hat{\mathbf x}^b_{1}\\
		\hat{\mathbf x}^b_{2}\\
		\vdots\\
		\hat{\mathbf x}^b_{T}
	\end{array}
	\right],\quad \mathbf X=\left[
	\begin{array}{cccc}
		\mathbf q(\hat{\mathbf x}^b_0)& \hat{\mathbf x}^b_{0}\\
		\mathbf q(\hat{\mathbf x}^b_1)& \hat{\mathbf x}^b_{1}\\
		\vdots & \vdots\\
		\mathbf q(\hat{\mathbf x}^b_{T-1})& \hat{\mathbf x}^b_{T-1}
	\end{array}
	\right] 
\end{equation*}
\end{small}
and
\begin{small}
\begin{equation*}
\quad \mathcal W=\left[
	\begin{array}{cc}
		\boldsymbol{\theta} \\
		\xi
	\end{array}
	\right],\quad \mathbf{e}=\left[
	\begin{array}{cccc}
		\mathbf e_0\\
		\mathbf e_1\\
		\vdots\\
		\mathbf e_{T-1}
	\end{array}
	\right].
\end{equation*}
\end{small}
Following this, the LS parameter estimates~\cite{Kailath2000} \ken{some reference for this result}, $ \hat{\mathcal{W}}$, are
\begin{equation}
	\hat{\mathcal{W}}=(\mathbf X^\top\mathbf X)^{-1}\mathbf X^\top\mathbf Z. 
\end{equation}
